|

### 2020-09-17 paper.Rmd
more edits

The sage display can be directly used in exploratory high dimensional data analysis
tasks.
We showed in the sketches example, that sage display decreases the number of overlapping points between classes and provides
better visual separation between classes compared to the regular tour. Furthermore, unlike some
non-linear dimension reduction (NLDR) techniques like t-SNE, the sage display still gives the viewer an accurate assessment of the size of a cluster, and their relative orientation.
The single cell RNA-seq case study uncovered clusters that were originally obscured by data piling but that are close in high dimensional space;

>>>>

The sage display is easily incorporated into exploratory high dimensional data analysis
tasks: classification, clustering, and search. For classification tasks,
as shown in the sketches example, the sage display decreases the number of 
overlapping points between classes and provides better visual separation between
classes compared to the regular tour.  For clustering tasks, as shown in the 
single cell RNA-seq example, the sage display uncovered clusters that were 
originally obscured by data piling. Furthermore, unlike some
non-linear dimension reduction (NLDR) techniques like t-SNE, the sage display 
still gives the viewer an accurate assessment of the size of a cluster, 
and their relative orientation. We learned that the highlighted 
The single cell RNA-seq case study uncovered clusters that were originally obscured by data piling;
